A Road Segment Prioritization Approach for Cycling Infrastructure

### 2022-09-01 README.Rmd
minor conclusion edits to emphasize big picture takeaways

This paper demonstrates an approach for prioritizing
investments in city-wide cycleway networks. The approach aims to respect
both the needs of the users and the ambitions of stakeholders working at
local or regional levels. The results, including detailed route network
maps based on current travel behaviour derived from OD data, can provide
an evidence-base for designing direct, connected,
and low-stress networks.

@@

The approach can identify not only where there is high
potential for cycling but also trade-offs between
stress levels (related to motor traffic) and directness.
The results can therefore be used as a basis for recommendations on
road space reallocation *and* new infrastructure to unlock potential cycling demand.
The approach encourages consideration of a wider range of preferences
and needs than previous approaches that focus only on absolute potential.
Moreover, the inclusion of egalitarian principles in scenarios of change
encourages investment in cycling infrastructure to
increase the connectivity of existing cycling infrastructure
*and* investment that addresses geographical and social inequalities.
This ability to address inequalities in network prioritization is particularly
important given research showing substantial *inequalities*
around transport provision in general and cycling uptake and investment
in particular [@lucas2016method; @vidaltortosa_infrastructure_2020].

>>>>

This paper demonstrates an approach for prioritizing
investments in city-wide cycleway networks. The approach aims to respect
both the needs of the users and the ambitions of stakeholders working at
local or regional levels. The results, including detailed route network
maps based on current travel behaviour derived from OD data, can provide
an evidence-base for designing direct, connected,
and low-stress networks. A core contribution of this approach is that it insures 
that investments in cycling infrastructure are distributed fairly between different 
communities in a city.

@@

The approach can identify not only where there is high
potential for cycling but also trade-offs between
stress levels (related to motor traffic) and directness.
The results can therefore be used as a basis for recommendations on
road space reallocation *and* new infrastructure to unlock potential cycling demand.
The approach encourages consideration of a wider range of preferences
and needs than previous approaches that focus only on absolute potential.
Moreover, the inclusion of egalitarian principles in scenarios of change
encourages investment in cycling infrastructure that addresses geographical and 
social inequalities. This is done by explicitly ensuring that infrastructure improvements 
are pursued in different parts of the city simultaneously. This approach compares well with one 
that focuses exclusively on maximizing the number of potential cycling trips that 
benefit from investment, showing that a fair distribution can be achieved without 
compromising on overall benefit. 
This ability to address inequalities in network prioritization is particularly
important given research showing substantial *inequalities*
around transport provision in general and cycling uptake and investment
in particular [@lucas2016method; @vidaltortosa_infrastructure_2020].
